A Formalization of Complete Discrete Valuation Rings and Local Fields

### 2023-09-05 CPP_paper/paper.tex

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  TODO
\end{abstract}

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  Local fields, and fields complete with respect to a discrete valuation, are essential objects in number theory.
  We formalize in Lean the basic theory of discretely valued fields. In particular, we prove that the unit ball of a field with a
  discrete valuation is a discrete valuation ring, and conversely, that the adic
  valuation on the field of fractions of a discrete valuation ring is discrete. We construct finite extensions of valuations and of discrete valuation
  rings, and prove some global-to-local results.

  Building on this general theory, we formalize the abstract definition and some fundamental properties of local fields, and show that finite extensions of the field $\QQ_p$ of $p$-adic numbers and of the field $\laurentseries$ of Laurent series over a finite field are local fields.

\end{abstract}
